---
title: "ScotSport - sports facilities in Scotland"
format: 
  dashboard:
    orientation: rows
    scrolling: true
    link-external-icon: true
    link-external-newwindow: true
    logo: images/scotsport-arthur-montford-houndstooth.png
    favicon: images/favicon.ico
    nav-buttons: 
      - icon: github
        href: https://github.com/dataquine/scotsport
    theme:
      light: [flatly, css/custom.scss]
      dark: [darkly, css/custom.scss]
server: shiny
date: today
include-in-header:
  # Workaround for favicon
  text: |
    <link rel="shortcut icon" href="images/favicon.ico" type="image/x-icon" />
    <link rel="icon" href="images/favicon.ico" type="image/x-icon">
    <link rel="icon" href="images/favicon-16x16.png" sizes="16×16">
    <link rel="icon" href="images/favicon-32x32.png" sizes="32×32">
    <link rel="icon" href="images/android-chrome-192x192.png" type="image/png" sizes="192x192">
    <link rel="icon" href="images/android-chrome-512x512.png" type="image/png" sizes="512x512">
    <link rel="apple-touch-icon" href="images/apple-touch-icon.png" sizes="180x180">
---
# {.sidebar}

**Last update:** `r date_updated`
---

```{r}
#| label: sidebar
selectInput("select_council", strong("Council areas:"),
  c("Choose one or more" = "", council_areas),
  multiple = TRUE
)
```
---
People per facility based on estimated population in 
**`r population_country$year`**

# Overview

## Row 

::: {.card .flow expandable=false}

`r textOutput ("home_area_names", inline = TRUE)`

:::

## Row

### Col {width=35%}

```{r}
#| label: total_facilities_areas
value_box(
  id = "valuebox_total_facilities_areas",
  title = "Total facilities",
  value = textOutput("total_facilities_areas", inline = TRUE),
  showcase = bs_icon("building"),
  showcase_layout = "left center",
  theme = scotsport_value_box_theme,
  class = "border"
)
```
```{r}
#| label: total_people_per_facility
value_box(
  title = "People per facility",
  value = textOutput("total_people_per_facility", inline = TRUE),
  showcase = bs_icon("person"),
  showcase_layout = "left center",
  theme = scotsport_value_box_theme,
  class = "border"
)
```
```{r}
#| label: home_total_towns_with_facilities
value_box(
  title = "Towns with facilities",
  value = textOutput("home_total_towns_with_facilities", inline = TRUE),
  showcase = bs_icon("bank"),
  showcase_layout = "left center",
  theme = scotsport_value_box_theme,
  class = "border"
)
```

### Col {width=65%}

### {.tabset}

```{r}
#| label: facilities
#| title: "Facilities"
#| padding: 0px
#| expandable: true
plotOutput("plot_scotland_area_facilities")
```
```{r}
#| label: people
#| title: "People"
#| padding: 0px
#| expandable: true
plotOutput("plot_scotland_area_people")
```

# Where

::: {.card .flow expandable=false}
`r textOutput ("where_area_names", inline = TRUE)`

**`r textOutput("where_total_towns_with_facilities", inline=TRUE)`** towns have
at least one facility. Choose a town to see a map. All locations are 
approximate. Click on pins to see more detail about the facility or circles with
numbers to see more facilities. +/- to zoom in/out.
:::

```{r}
#| content: card-toolbar
#| label: select-town
uiOutput("ui_select_town")
```

```{r}
#| label: leaflet-map-town
#| padding: 0px
#| expandable: true
#| fig-alt: "TODO"
leafletOutput("map_town")
```

# Type

`r textOutput ("type_area_names", inline = TRUE)`

## {.tabset}

```{r}
#| label: type-plot
#| title: "Type"
plotOutput("plot_facility_type")
```
```{r}
#| label: type-subtype-table
#| title: "Subtype"
gt::gt_output(outputId = "facility_type_table")
```

# Address 

```{r}
#| label: address-table
#| padding: 0.5em
gt::gt_output(outputId = "facility_detail_table")
```

# About

```{r}
#| label: about-markdown
#| fill: false
# Reuse the same readme file for the repository
htmltools::includeMarkdown("README.md")
```
